Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-07-08 tex/merf/TALMajor/results.tex
final version

We evaluated ANGE with
Musnad Ahmad, a hadith book, where we constructed an annotated 
golden reference containing 1,865 words.
We evaluated ATEEMA 
with articles from issues of  the Lebanese 
Al-Akhbar newspaper where we constructed 
an annotated golden reference containing 1,677 words. 
For the genealogical tree extraction we used 
an extract from the Genesis biblical text with 1,227 words.
Finally, we used an annotated article from the Lebanese Assafir
newspaper with 1,399 words to evaluate the NUMNORM case study
\footnote{available at \url{http://www.assafir.com} and 
\url{http://www.al-akhbar.com}.}. 
%
In the online appendix%
~\footnote{available at ~\url{-omitted-for-anonymity-}}%http://webfea.fea.aub.edu.lb/fadi/pdfs/merfappendix.pdf
, we report on eight additional \framework case studies.
Manual annotators inspected the outcome and provided corrections where tools 
made mistakes.
The corrections form the manual gold annotation that we compared against.

>>>>

We evaluated ANGE with
Musnad Ahmad, a hadith book, where we constructed an annotated 
golden reference containing 1,865 words.
We evaluated ATEEMA 
with articles from issues of  the Lebanese 
Al-Akhbar newspaper where we constructed 
an annotated golden reference containing 1,677 words. 
For the genealogical tree extraction we used 
an extract from the Genesis biblical text with 1,227 words.
Finally, we used an annotated article from the Lebanese Assafir
newspaper with 1,399 words to evaluate the NUMNORM case study
\footnote{available at \url{http://www.assafir.com} and 
\url{http://www.al-akhbar.com}.}. 
%
In the online appendix%
~\footnote{available at ~\url{http://research-fadi.aub.edu.lb/pdfs/merfappendix.pdf}}
, we report on eight additional \framework case studies.
Manual annotators inspected the outcome and provided corrections where tools 
made mistakes.
The corrections form the manual gold annotation that we compared against.
